### 2024-07-18 Article/Article.tex
typos

Next we'll give a~self-contained (independent of~other major theorems) proof of~this theorem.
For~this purpose we need an~auxiliary statement.

@@

    Take an~arbitrary character $f$. Since it is a~homomorphism, $f(1_G) = 1$
    where $1_G$ is an~identity element in the~group $G$. But then if $\alpha f = 0$, then
    $\alpha = \alpha \cdot 1 = \alpha \cdot f(1_G) = 0$ what proves the~base case.

@@

    Since the~equality is reflexive, symmetric and transitive, the~system of~all equations $z^{i_{k, i}} = z^{i_{k, j}}$
    is equivalent to~the~system of~$N$ equations composed of consecutive indices:
    $$
        z^{i_{1, 1}} = z^{i_{1, 2}}, z^{i_{1, 2}} = z^{i_{1, 3}}, \ldots, z^{i_{1, N_1 - 1}} = z^{i_{1, N_1}}, z^{i_{2, 1}} = z^{i_{2, 2}}, \ldots, z^{i_{m, N_m - 1}} = z^{i_{m, N_m}}.
    $$
    We denote the~set of solutions of~this system by~$A$.

    Let us show that $A$ coincides with $H$. Indeed, let $z \in H$. Then, as noted before,
    by~definition of~$I_k$ is is true that $z^{i_{k, j}} = \chi_k(z) = z^{i_{k, j + 1}}$;
    that is, $z \in A$ and $H \subseteq A$.

    Conversely, let $z \in A$. Then by~definition of~$A$ we have $z^{i_{k, j_1}} = z^{i_{k, j_1 + 1}} = \ldots = z^{i_{k, j_2 - 1}} = z^{i_{k, j_2}}$
    for all $1 \leq j_1 \leq j_2 \leq N_k$. Choose a~representative $i_k \in I_k$ in each~$I_k$
    and combine like terms:
    $$
        P_j(z) = \sum_{k = 1}^{m} \left( \sum_{i \in I_k} a_{ji} \right) z^{i_k} = \sum_{k = 1}^{m} 0 \cdot z^{i_k} = 0,
    $$
    what means $z \in H$, that is, $A \subseteq H$.

@@

For~an abelian group $G$ and vectors $\alpha_1, \ldots, \alpha_n \in \mathbb{Z}^k$ consider the~mapping
$\phi_\alpha(t) = (t^{\alpha_1}, t^{\alpha_2}, \ldots, t^{\alpha_n})$ from~$G^k$ to~$G^n$ where $\alpha$ is~a~matrix
with rows $\alpha_i$. Since $(t_1 \cdot t_2)^{\alpha_i} = t_1^{\alpha_i} \cdot t_2^{\alpha_i}$,
$\phi_\alpha$ is a~homomorphism. Further we will that if $K$ is a~field, then the~mapping $\phi_\alpha$
for the~group $G = K^\times$ defines \textit{a~parameterization} of~some algebraic group.

@@

    On~the~right side we have the~sum of $\sum_{k = 1}^n C^n_k > 0$ units. Since $\mathrm{char}(K) = 0$,
    it is not equal to zero, that is, $2^n - 1 \neq 0$.
\hfill$\Box$\medskip

@@

    $\phi_\alpha(t) = 1$ means that $t^{\alpha_i} = 1$ for all $1 \leq i \leq n$.
    Fix $1 \leq j \leq k$ and raise to~the power of~$b^j_i$ both sides of~this equation:
    $t^{b^j_i \alpha_i} = (t^{\alpha_i})^{b^j_i} = 1^{b^j_i} = 1$.
    Finally, multiply the~obtained equations:
    $
        t_j = t^{e_j} = t^{b^j_1 \alpha_1 + \ldots + b^j_n \alpha_n} = t^{b^j_1 \alpha_1} \ldots t^{b^j_n \alpha_n} = 1 \cdot \ldots \cdot 1 = 1.
    $
\hfill$\Box$\medskip

Now we will show that the~obtained necessary condition is also sufficient for~the~group $G = {\mathbb{C}^\times}$.

@@

\medskip\noindent\textbf{Theorem} (on~the~existence of Smith normal form).\emph{
    $$
        \forall \alpha \in \mathbb{Z}^{m \times n}{:}\
        \exists \beta_1 \in \mathrm{GL}^m(\mathbb{Z}), \beta_2 \in \mathrm{GL}^n(\mathbb{Z}){:} \
        \exists \varepsilon_1, \ldots, \varepsilon_r \in \mathbb{Z} \setminus \{0\}{:} \
        \beta_1 \alpha \beta_2 = \mathrm{diag}^{m \times n}_r(\varepsilon_1, \ldots, \varepsilon_r),
    $$
    where $\varepsilon_1 \mid \varepsilon_2 \mid \ldots \mid \varepsilon_r$ (the so~called invariant factors) and $r = \mathrm{rank}(\alpha)$.
}\medskip

Since the numbers $\varepsilon_1$, $\ldots$, $\varepsilon_r$ are chosen in a~unique way up to the~invertible element,
that is, up to $\pm 1$ in~case of $\mathbb{Z}$, we can always choose them positive. For them we denote
the~matrix $\mathrm{diag}^{m \times n}_r(\varepsilon_1, \ldots, \varepsilon_r)$ by~$\mathrm{SNF}(\alpha)$.

@@

\medskip\noindent\textbf{Lemma~6.}\emph{
    $\phi_\alpha$ for $\alpha \in \mathbb{Z}^{n \times k}$ can be expressed as some image $\mathrm{Im}(\phi_\beta)$
    if the~mappings $g \mapsto g^{\varepsilon_i}$ are surjective in~$G$ for all $\varepsilon_i$ из~$\mathrm{SNF}(\alpha)$.
}\medskip

@@

    Consider $\delta = \mathrm{diag}^{n \times r}_r(1, \ldots, 1)$ и~$\alpha' = \beta^{-1} \delta$.
    $\phi_{\alpha'}$ is injective since it is a~composition of injective functions. On~the~other hand, it is obvious that:
    $$
        \mathrm{Im}(\phi_\alpha) = \phi_{\beta_1^{-1}} (\phi_\varepsilon (\phi_{\beta_2^{-1}} (G^k)))
                                 = \phi_{\beta_1^{-1}} (\phi_\varepsilon (G^k))
                                 = \phi_{\beta_1^{-1}} (\phi_{\delta} (G^r))
                                 = \mathrm{Im}(\phi_{\alpha'}).
    $$

@@

To~prove the~criterion described before, consider the~number $\Pi(\alpha) = |\omega_K(\varepsilon)|$
where $|G|$ is the~order of the~group $G$. $|G \times H| = |G| |H|$, so $\Pi(\alpha) = |\omega_K(\varepsilon_1)| \cdot \ldots \cdot |\omega_K(\varepsilon_r)|$.
Since $\omega(n)$ is isomorphic to~$\mathbb{Z} / n \mathbb{Z}$, in~case of the~field $K = \mathbb{C}$ it is also true that
$\Pi(\alpha) = \varepsilon_1 \cdot \ldots \cdot \varepsilon_r$.

@@

In~any abelian group $G$ there is naturally defined multiplication by~integers.
For a~vector $\alpha = (\alpha_1, \ldots, \alpha_k) \in \mathbb{Z}^k$ and element $g \in G$
by~$g \alpha$ we mean the~vector $(\alpha_1 g, \ldots, \alpha_k g) \in G^k$. We say that
the~collection of~vectors $\alpha_1, \ldots, \alpha_n \in \mathbb{Z}^k$ is \textit{linearly independent
over an~abelian group} if
$$
    \forall g_1, \ldots, g_n \in G{:}\ g_1 \alpha_1 + \ldots + g_n \alpha_n = 0 \Rightarrow g_1 = \ldots = g_n = 0.
$$

@@

\noindent{\it Proof.} It follows directly from the~fact that injectivity of a~homomorphism is equivalent to the~triviality of~its kernel.
\hfill$\Box$\medskip

@@

\medskip\noindent\textbf{Lemma~8.}\emph{
    Let $G$ and $H$ be abelian groups. $\mu_1,\allowbreak \ldots,\allowbreak \mu_n \in \mathbb{Z}^k$ are linearly independent
    over $G \times H$ if and only if the are linearly independent over $G$ and over $H$.
}\medskip

@@

    It is known that $\mathbb{R}$ is an~(infinite-dimensional) vector space over $\mathbb{Q}$, and any vector space has
    a~(Hamel) basis under assumption of the~axiom of~choice~\cite{Brbk70}. Using this, let us fix a~Hamel basis $B$ for $\mathbb{R}$
    over $\mathbb{Q}$. Let us decompose $r_i$ by this basis:
    $$
        r_i = q_i^1 b_1 + \ldots + q_i^s b_s
    $$
    where $q_i^j \in \mathbb{Q}$ and $b_j \in B$. There are finitely many vectors $r_i$,
    so the~set of basis vectors $b_j$ for them can be chosen to be the~same.
    Let us substitute the~decomposition into the~linear combination:
    \begin{align*}
        r_1 \mu_1 + \ldots + r_n \mu_n & = (q_1^1 b_1 + \ldots + q_1^s b_s) \mu_1 + \ldots + (q_n^1 b_1 + \ldots + q_n^s b_s) \mu_n \\
                                       & = (q_1^1 \mu_1 + \ldots + q_n^1 \mu_n) b_1 + \ldots + (q_1^s \mu_1 + \ldots + q_n^s \mu_n) b_s \\
                                       & = 0.
    \end{align*}

    In each coordinate we obtain a~rational linear combination of the~numbers $b_j$ equal to zero.
    By~virtue of linear independence, all these coordinates are equal to zero, so we have:
    $q_1^j \mu_1 + \ldots + q_n^j \mu_n = 0$.

@@

For a~number $d \in \mathbb{Z}$ and a~vector $x \in \mathbb{Z}^k$ by $d \mid x$ we mean that $d \mid x_i$ for all $1 \leq i \leq k$
or, equivalently, $d \mid \gcd(x_1, \ldots, x_n)$.

@@

    Next, fix a~power $\beta \in \mathbb{N}$ and a~prime number $p$.
    Since $x_1 \mu_1 + \ldots + x_n \mu_n$ is divisible $p^\beta$,
    it is also divisible by~$p$, so it follow from the~premise that $p \mid x$.

>>>>

Next, we'll give a~self-contained (independent of~other major theorems) proof of~this theorem.
For~this purpose, we need an~auxiliary statement.

@@

    Take an~arbitrary character $f$. Since it is a~homomorphism, $f(1_G) = 1$
    where $1_G$ is an~identity element in the~group $G$. But then if $\alpha f = 0$, then
    $\alpha = \alpha \cdot 1 = \alpha \cdot f(1_G) = 0$, which proves the~base case.

@@

    Since the~equality is reflexive, symmetric, and transitive, the~system of~all equations $z^{i_{k, i}} = z^{i_{k, j}}$
    is equivalent to~the~system of~$N$ equations composed of consecutive indices:
    $$
        z^{i_{1, 1}} = z^{i_{1, 2}}, z^{i_{1, 2}} = z^{i_{1, 3}}, \ldots, z^{i_{1, N_1 - 1}} = z^{i_{1, N_1}}, z^{i_{2, 1}} = z^{i_{2, 2}}, \ldots, z^{i_{m, N_m - 1}} = z^{i_{m, N_m}}.
    $$
    We denote the~set of solutions of~this system by~$A$.

    Let us show that $A$ coincides with $H$. Indeed, let $z \in H$. Then, as noted before,
    by~definition of~$I_k$ it is true that $z^{i_{k, j}} = \chi_k(z) = z^{i_{k, j + 1}}$;
    that is, $z \in A$ and $H \subseteq A$.

    Conversely, let $z \in A$. Then by~definition of~$A$ we have $z^{i_{k, j_1}} = z^{i_{k, j_1 + 1}} = \ldots = z^{i_{k, j_2 - 1}} = z^{i_{k, j_2}}$
    for all $1 \leq j_1 \leq j_2 \leq N_k$. Choose a~representative $i_k \in I_k$ in each~$I_k$
    and combine like terms:
    $$
        P_j(z) = \sum_{k = 1}^{m} \left( \sum_{i \in I_k} a_{ji} \right) z^{i_k} = \sum_{k = 1}^{m} 0 \cdot z^{i_k} = 0,
    $$
    which means $z \in H$, that is, $A \subseteq H$.

@@

For~an abelian group $G$ and vectors $\alpha_1, \ldots, \alpha_n \in \mathbb{Z}^k$ consider the~mapping
$\phi_\alpha(t) = (t^{\alpha_1}, t^{\alpha_2}, \ldots, t^{\alpha_n})$ from~$G^k$ to~$G^n$ where $\alpha$ is~a~matrix
with rows $\alpha_i$. Since $(t_1 \cdot t_2)^{\alpha_i} = t_1^{\alpha_i} \cdot t_2^{\alpha_i}$,
$\phi_\alpha$ is a~homomorphism. Further we will see that if $K$ is a~field, then the~mapping $\phi_\alpha$
for the~group $G = K^\times$ defines \textit{a~parameterization} of~some algebraic group.

@@

    On~the~right side we have the~sum of $\sum_{k = 1}^n C^n_k > 0$ units. Since $\mathrm{char}(K) = 0$,
    this sum is not equal to zero, that is, $2^n - 1 \neq 0$.
\hfill$\Box$\medskip

@@

    $\phi_\alpha(t) = 1$ means $t^{\alpha_i} = 1$ for all $1 \leq i \leq n$.
    Fix $1 \leq j \leq k$ and raise both sides of~this equation to~the power of~$b^j_i$:
    $t^{b^j_i \alpha_i} = (t^{\alpha_i})^{b^j_i} = 1^{b^j_i} = 1$.
    Finally, multiply the~obtained equations:
    $
        t_j = t^{e_j} = t^{b^j_1 \alpha_1 + \ldots + b^j_n \alpha_n} = t^{b^j_1 \alpha_1} \ldots t^{b^j_n \alpha_n} = 1 \cdot \ldots \cdot 1 = 1.
    $
\hfill$\Box$\medskip

Now we will show that the~obtained necessary condition is also sufficient for the~group $G = {\mathbb{C}^\times}$.

@@

\medskip\noindent\textbf{Theorem} (on~the~existence of Smith normal form).\emph{
    $$
        \forall \alpha \in \mathbb{Z}^{m \times n}{:}\
        \exists \beta_1 \in \mathrm{GL}^m(\mathbb{Z}), \beta_2 \in \mathrm{GL}^n(\mathbb{Z}){:} \
        \exists \varepsilon_1, \ldots, \varepsilon_r \in \mathbb{Z} \setminus \{0\}{:} \
        \beta_1 \alpha \beta_2 = \mathrm{diag}^{m \times n}_r(\varepsilon_1, \ldots, \varepsilon_r),
    $$
    where $\varepsilon_1 \mid \varepsilon_2 \mid \ldots \mid \varepsilon_r$ (the so-called invariant factors) and $r = \mathrm{rank}(\alpha)$.
}\medskip

Since the numbers $\varepsilon_1$, $\ldots$, $\varepsilon_r$ are chosen in a~unique way up to the~invertible element,
that is, up to $\pm 1$ in the~case of $\mathbb{Z}$, we can always choose them positive. For them we denote
the~matrix $\mathrm{diag}^{m \times n}_r(\varepsilon_1, \ldots, \varepsilon_r)$ by~$\mathrm{SNF}(\alpha)$.

@@

\medskip\noindent\textbf{Lemma~6.}\emph{
    $\phi_\alpha$ for $\alpha \in \mathbb{Z}^{n \times k}$ can be expressed as some image $\mathrm{Im}(\phi_\beta)$
    if the~mappings $g \mapsto g^{\varepsilon_i}$ are surjective in~$G$ for all $\varepsilon_i$ from $\mathrm{SNF}(\alpha)$.
}\medskip

@@

    Consider $\delta = \mathrm{diag}^{n \times r}_r(1, \ldots, 1)$ and $\alpha' = \beta^{-1} \delta$.
    $\phi_{\alpha'}$ is injective since it is a~composition of injective functions. On~the~other hand, it is obvious that:
    $$
        \mathrm{Im}(\phi_\alpha) = \phi_{\beta_1^{-1}} (\phi_\varepsilon (\phi_{\beta_2^{-1}} (G^k)))
                                 = \phi_{\beta_1^{-1}} (\phi_\varepsilon (G^k))
                                 = \phi_{\beta_1^{-1}} (\phi_{\delta} (G^r))
                                 = \mathrm{Im}(\phi_{\alpha'}).
    $$

@@

To~prove the~criterion described before, consider the~number $\Pi(\alpha) = |\omega_K(\varepsilon)|$
where $|G|$ is the~order of the~group $G$. $|G \times H| = |G| |H|$, so $\Pi(\alpha) = |\omega_K(\varepsilon_1)| \cdot \ldots \cdot |\omega_K(\varepsilon_r)|$.
Since $\omega(n)$ is isomorphic to~$\mathbb{Z} / n \mathbb{Z}$, in the~case of the~field $K = \mathbb{C}$ it is also true that
$\Pi(\alpha) = \varepsilon_1 \cdot \ldots \cdot \varepsilon_r$.

@@

In~any abelian group $G$ there is naturally defined multiplication by~integers.
For a~vector $\alpha = (\alpha_1, \ldots, \alpha_k) \in \mathbb{Z}^k$ and element $g \in G$
we mean by~$g \alpha$ the~vector $(\alpha_1 g, \ldots, \alpha_k g) \in G^k$. We say that
the~collection of~vectors $\alpha_1, \ldots, \alpha_n \in \mathbb{Z}^k$ is \textit{linearly independent
over an~abelian group} if
$$
    \forall g_1, \ldots, g_n \in G{:}\ g_1 \alpha_1 + \ldots + g_n \alpha_n = 0 \Rightarrow g_1 = \ldots = g_n = 0.
$$

@@

\noindent{\it Proof.} It follows directly from the~fact that the~injectivity of a~homomorphism is equivalent to the~triviality of~its kernel.
\hfill$\Box$\medskip

@@

\medskip\noindent\textbf{Lemma~8.}\emph{
    Let $G$ and $H$ be abelian groups. $\mu_1,\allowbreak \ldots,\allowbreak \mu_n \in \mathbb{Z}^k$ are linearly independent
    over $G \times H$ if and only if they are linearly independent over $G$ and over $H$.
}\medskip

@@

    It is known that $\mathbb{R}$ is an~(infinite-dimensional) vector space over $\mathbb{Q}$, and any vector space has
    a~(Hamel) basis under the~assumption of the~axiom of~choice~\cite{Brbk70}. Using this, let us fix a~Hamel basis $B$ for $\mathbb{R}$
    over $\mathbb{Q}$. Let us decompose $r_i$ by this basis:
    $$
        r_i = q_i^1 b_1 + \ldots + q_i^s b_s
    $$
    where $q_i^j \in \mathbb{Q}$ and $b_j \in B$. There are finitely many vectors $r_i$,
    so the~set of basis vectors $b_j$ for them can be chosen to be the~same.
    Let us substitute the~decomposition into the~linear combination:
    \begin{align*}
        r_1 \mu_1 + \ldots + r_n \mu_n & = (q_1^1 b_1 + \ldots + q_1^s b_s) \mu_1 + \ldots + (q_n^1 b_1 + \ldots + q_n^s b_s) \mu_n \\
                                       & = (q_1^1 \mu_1 + \ldots + q_n^1 \mu_n) b_1 + \ldots + (q_1^s \mu_1 + \ldots + q_n^s \mu_n) b_s \\
                                       & = 0.
    \end{align*}

    We obtain in each coordinate a~rational linear combination of the~numbers $b_j$ equal to zero.
    By~virtue of linear independence, all these coordinates are equal to zero, so we have:
    $q_1^j \mu_1 + \ldots + q_n^j \mu_n = 0$.

@@

For a~number $d \in \mathbb{Z}$ and a~vector $x \in \mathbb{Z}^k$ we mean by $d \mid x$ that $d \mid x_i$ for all $1 \leq i \leq k$
or, equivalently, $d \mid \gcd(x_1, \ldots, x_n)$.

@@

    Next, fix a~power $\beta \in \mathbb{N}$ and a~prime number $p$.
    Since $x_1 \mu_1 + \ldots + x_n \mu_n$ is divisible $p^\beta$,
    it is also divisible by~$p$, so it follows from the~premise that $p \mid x$.
